Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-01-17 SCCAbstract_SDSS2022-knitr.Rnw
cite not citep
Updating more about the GDL piece

\svp{As part of this project, we have assembled a large set of publicly available data (primarily from \url{data.iowa.gov}), but we are careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. We select a small subset of towns (out of the 999 towns in Iowa) and a small subset of variables of interest to start with, and then allow the user to increase the complexity of the display in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload \citep{few}.}

@@

Our current work incorporates the ideas of GDL, in which dashboard design has been used to display a panel with vital statistics, ensuring that the town's analyst small town is the center of focus. The vital statistics highlight the town's financial health and the shortest distances from the city center to critical resources, such as the fire department, hospital, post offices, and public schools. The dashboard includes Quality of Life (QoL) Metrics and the financial health of the small town. Based on the number of variables used to ensure that the dashboard is extensive and valuable, we implemented parallel coordinate plots to show comparisons between the focus small town with the five similar towns. A parallel (coordinates) plot allowed our town analyst to compare the essential features of several individual towns on a set of numeric and categorical variables collected. Historically, parallel coordinate plots have been used in air traffic control to help with collision avoidance algorithms but have been adapted in the statistical data visualization space, emphasizing three critical considerations: the order, the rotation, and the scaling of the axes. Our coordinate plots will display variables categorically and numerically by scaling the data.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=75mm]{SCC_Dashboard.png}
\caption{Rural Smart EDA Dashboard Design}
\end{figure}

>>>>

\svp{As part of this project, we have assembled a large set of publicly available data (primarily from \url{data.iowa.gov}), but we are careful with how we present this data because it would be easy to overwhelm the user with small details that mask the bigger picture. We select a small subset of towns (out of the 999 towns in Iowa) and a small subset of variables of interest to start with, and then allow the user to increase the complexity of the display in accordance with their interest. This avoids some of the pitfalls of dashboard design that can easily lead to user overload \cite{few}.}

@@

Our current work incorporates the ideas of GDL, in which our dashboard design has been used to display a panel with vital statistics, ensuring that the town leaders of a small town is the center of focus on the dashboard. The vital statistics highlight the town's financial health and the shortest distances from the city center to critical resources, such as the fire department, hospital, post offices, and public schools. To complement the Rural Shrink Smart NSF Grant, our dashboard includes Quality of Life (QoL) Metrics, to help identify communities social networks along with financial health data collected to ensure a robust identification of our small towns.

To restate, our dashboard incorporates an extensive number of variables used to ensure a valuable tool to town leaders, we implemented parallel coordinate plots to show comparisons between the user's small town with the five similar towns. The user has an option to select similarities, such as economy, location and size, allowing the town leaders the flexibility to guided their interests in the small town. As stated by DeDonno \cite{dedonno}, our dashboard leverages hints for the town leaders to learn through feedback on the next steps to take in their towns.

A parallel (coordinates) plot allowed our town analyst to compare the essential features of several individual towns on a set of numeric and categorical variables collected. Historically, parallel coordinate plots have been used in air traffic control to help with collision avoidance algorithms but have been adapted in the statistical data visualization space, emphasizing three critical considerations: the order, the rotation, and the scaling of the axes. Our coordinate plots will display variables categorically and numerically by scaling the data.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=75mm]{SCC_Dashboard_pcp2.png}
\caption{Rural Smart EDA Dashboard Design}
\end{figure}
